Fish Comparisons Simple Models

### 2022-05-18 Fish Data Analysis/comp_fish_simple_models.Rmd
Update before I do my work making the 3D processor

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(car)
library(viridis)
library(boot)
library(mgcv)
library(forcats)
library(ggpubr)
```

@@

Sets up the functions that will be used later 
```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan(mean(sin(deg2rad(x)))/mean(cos(deg2rad(x)))))}

@@

comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(Distance <= 4) %>%
                           filter(abs(Speed_Diff) <= 6) %>% 
                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
                           mutate(fold_heading_diff = abs(fold_angle_neg_180_180_to_neg_90_90(Heading_Diff))) %>%
                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0)) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Flow 0","Flow 2"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(rad_Angle = Angle) %>%
                           mutate(sin_Angle = sin(rad_Angle), cos_Angle = cos(rad_Angle)) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", ")))

@@

sum_comp_data <- comp_data %>% mutate(X_Distance = round_any(X_Distance,0.25), 
                                      Y_Distance = round_any(abs(Y_Distance),0.25)) %>%
                               group_by(Flow,Ablation,Darkness,X_Distance,Y_Distance) %>%
                               summarise(Speed_Diff = mean(Speed_Diff),
                                         Heading_Diff = ang_mean(Heading_Diff),
                                         Sync = mean(Sync),
                                         Fold_Heading_Diff = mean(fold_heading_diff),
                                         Is_Aligned = mean(Is_Aligned),
                                         Is_Reversed = mean(Is_Reversed))

@@

comp_data_NND <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat.Num) %>%
                                                                 filter(Distance == min(Distance)) %>%
                                                                 ungroup()

comp_data_near_3 <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat.Num) %>%
                                                                 slice_min(Distance, n = 3) %>%
                                                                 ungroup() %>%
                                                                 distinct(Distance, .keep_all= TRUE)
```

@@

```{r}
speed_anova <- aov(Speed_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_3)

@@

heading_anova <- aov(fold_heading_diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_3)

@@

sync_anova <- aov(Sync ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_3)

@@

Anova(dist_anova)
```

```{r}
ggplot(comp_data_near_3, aes(x = cos(deg2rad(Angle))))+
  geom_histogram()+
  facet_wrap(~ Flow + Ablation + Darkness)

ggplot(comp_data_near_3, aes(x = sin(deg2rad(Angle))))+
  geom_histogram()+
  facet_wrap(~ Flow + Ablation + Darkness)
```

```{r}
ggplot(comp_data_near_3, aes(x = Flow, y = Speed_Diff, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Speed Difference") +
  xlab("") +
  ylab("Speed Difference (BL/s)") +
  ylim(-0.1,2.5) +
  theme_light()

ggplot(comp_data_near_3, aes(x = Flow, y = fold_heading_diff, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Heading Difference") +
  xlab("") +
  ylab("Heading Difference (Degrees)") +
  theme_light()

@@

ggplot(comp_data_near_3, aes(x = Flow, y = Angle, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Nearest Neighbor Bearing") +
  xlab("") +
  ylab("Nearest Neighbor Bearing (Degrees)") +
  scale_y_continuous(breaks = c(30,60,90,120,150)) +
  theme_light()

Trying GAMs

```{r}
speed_gam <- gam(Speed_Diff ~ s(Distance,Angle,by=Flow_Ablation_Darkness),
                              data = comp_data_near_3)

summary(speed_gam)

heading_gam <- gam(fold_heading_diff ~ s(Distance,Angle,by=Flow_Ablation_Darkness),
                              data = comp_data_near_3)

summary(heading_gam)

sync_gam <- gam(Sync ~ s(Distance,Angle,by=Flow_Ablation_Darkness),
                              data = comp_data_near_3)

summary(sync_gam)
```

Now we make some predictions for this.
```{r}
d <- seq(from = 0, to = 3, by = 0.1)
a <- seq(from = 0, to = 180, by = 10)

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(car)
library(viridis)
library(boot)
library(mgcv)
library(forcats)
library(ggpubr)
library(mgcViz)
```

@@

Sets up the functions that will be used later 
```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

@@

comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(Distance <= 4) %>%
                           filter(abs(Speed_Diff) <= 6) %>% 
                           #mutate(Speed_Diff = abs(Speed_Diff)) %>%
                           mutate(rad_Heading = deg2rad(Heading_Diff)) %>%
                           mutate(sin_Heading = sin(rad_Heading), cos_Heading = cos(rad_Heading)) %>%
                           #mutate(fold_heading_diff = abs(fold_angle_neg_180_180_to_neg_90_90(Heading_Diff))) %>%
                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0)) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(rad_Angle = deg2rad(Angle)) %>%
                           mutate(sin_Angle = sin(rad_Angle), cos_Angle = cos(rad_Angle)) %>%
                           mutate(Flow_Ablation = factor(paste(Flow,Ablation,sep=", "))) %>%
                           mutate(Flow_Darkness = factor(paste(Flow,Darkness,sep=", "))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", ")))

@@

sum_comp_data <- comp_data %>% mutate(X_Distance = round_any(X_Distance,0.25), 
                                      Y_Distance = round_any(abs(Y_Distance),0.25)) %>%
                               group_by(Flow,Ablation,Darkness,X_Distance,Y_Distance) %>%
                               summarise(Speed_Diff = mean(Speed_Diff),
                                         Heading_Diff = ang_mean(Heading_Diff),
                                         Sync = mean(Sync),
                                         #Fold_Heading_Diff = mean(fold_heading_diff),
                                         Is_Aligned = mean(Is_Aligned),
                                         Is_Reversed = mean(Is_Reversed))

@@

comp_data_NND <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat_Num) %>%
                                                                 filter(Distance == min(Distance)) %>%
                                                                 ungroup()

comp_data_near_3 <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat_Num) %>%
                                                                 slice_min(Distance, n = 3) %>%
                                                                 ungroup() %>%
                                                                 distinct(Distance, .keep_all= TRUE)
```

@@

```{r}
speed_anova <- aov(Speed_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_NND)

@@

heading_anova <- aov(Heading_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_NND)

@@

sync_anova <- aov(Sync ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_NND)

@@

Anova(angle_anova)
```

```{r}
ggplot(comp_data_near_3, aes(x = Flow, y = Speed_Diff, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Speed Difference") +
  xlab("") +
  ylab("Speed Difference (BL/s)") +
  #ylim(-0.1,2.5) +
  theme_light()

#rad2deg(atan(sin_Heading/cos_Heading))

ggplot(comp_data_near_3, aes(x = Flow, y = Heading_Diff, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_violin(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Heading Difference") +
  xlab("") +
  ylab("Heading Difference (Degrees)") +
  #scale_y_continuous(breaks = c(-90,-60,-30,0,30,60,90)) +
  theme_light()

@@

#rad2deg(atan2(sin_Angle,cos_Angle))

ggplot(comp_data_near_3, aes(x = Flow, y = Angle, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_violin(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Nearest Neighbor Bearing") +
  xlab("") +
  ylab("Nearest Neighbor Bearing (Degrees)") +
  #scale_y_continuous(breaks = c(-90,-60,-30,0,30,60,90)) +
  theme_light()

```
 Just nearest Fish Speed Diff

```{r}
comp_data_near_1 <- bind_rows(comp_data, comp_data_switch_fish) %>% group_by(Year,Month,Day,Trial,Fish1,Tailbeat_Num) %>%
                                                                 slice_max(Distance, n = 1) %>%
                                                                 ungroup() %>%
                                                                 distinct(Distance, .keep_all= TRUE)

speed_anova_nn <- aov(Speed_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data_near_1)

Anova(speed_anova_nn)

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))

ggplot(comp_data_near_1, aes(x = interaction(Ablation,Darkness,sep=", "), y = Speed_Diff, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_violin(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Nearest Speed Diff") +
  xlab("") +
  ylab("Speed Difference (BL/s)") +
  theme_light() +
  facet_wrap(~ Flow, strip.position = "bottom")+
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  #stat_compare_means(comparisons = my_comparisons, label.y = c(7.5,8.5), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

Trying ggpubr

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark") )

ggplot(comp_data_near_3, aes(x = interaction(Ablation,Darkness,sep=", "), y = Distance, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c("#EEEEEE", "#4CB944", "#00A7E1")) +
  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND)") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light() +
  facet_wrap(~ Flow)+
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  stat_compare_means(comparisons = my_comparisons, label.y = c(4.5), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

So we need to make all the possible GLMs for these variables and then compare them in order to see which model does best in order to see what actually has effects
```{r}
# speed_gam_d <- gam(Speed_Diff ~ s(Distance), data = comp_data_near_3)
# speed_gam_d_f <- gam(Speed_Diff ~ s(Distance,by=Flow), data = comp_data_near_3)
# speed_gam_d_a <- gam(Speed_Diff ~ s(Distance,by=Ablation), data = comp_data_near_3)
# speed_gam_d_d <- gam(Speed_Diff ~ s(Distance,by=Darkness), data = comp_data_near_3)
# speed_gam_d_fa <- gam(Speed_Diff ~ s(Distance,by=Flow_Ablation), data = comp_data_near_3)
# speed_gam_d_fd <- gam(Speed_Diff ~ s(Distance,by=Flow_Darkness), data = comp_data_near_3)
# speed_gam_d_fda <- gam(Speed_Diff ~ s(Distance,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# speed_gam_ca <- gam(Speed_Diff ~ s(cos_Angle), data = comp_data_near_3)
# speed_gam_ca_f <- gam(Speed_Diff ~ s(cos_Angle,by=Flow), data = comp_data_near_3)
# speed_gam_ca_a <- gam(Speed_Diff ~ s(cos_Angle,by=Ablation), data = comp_data_near_3)
# speed_gam_ca_d <- gam(Speed_Diff ~ s(cos_Angle,by=Darkness), data = comp_data_near_3)
# speed_gam_ca_fa <- gam(Speed_Diff ~ s(cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
# speed_gam_ca_fd <- gam(Speed_Diff ~ s(cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
# speed_gam_ca_fda <- gam(Speed_Diff ~ s(cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# speed_gam_sa <- gam(Speed_Diff ~ s(sin_Angle), data = comp_data_near_3)
# speed_gam_sa_f <- gam(Speed_Diff ~ s(sin_Angle,by=Flow), data = comp_data_near_3)
# speed_gam_sa_a <- gam(Speed_Diff ~ s(sin_Angle,by=Ablation), data = comp_data_near_3)
# speed_gam_sa_d <- gam(Speed_Diff ~ s(sin_Angle,by=Darkness), data = comp_data_near_3)
# speed_gam_sa_fa <- gam(Speed_Diff ~ s(sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
# speed_gam_sa_fd <- gam(Speed_Diff ~ s(sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
# speed_gam_sa_fda <- gam(Speed_Diff ~ s(sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# speed_gam_dca <- gam(Speed_Diff ~ s(Distance,cos_Angle), data = comp_data_near_3)
# speed_gam_dca_f <- gam(Speed_Diff ~ s(Distance,cos_Angle,by=Flow), data = comp_data_near_3)
# speed_gam_dca_a <- gam(Speed_Diff ~ s(Distance,cos_Angle,by=Ablation), data = comp_data_near_3)
# speed_gam_dca_d <- gam(Speed_Diff ~ s(Distance,cos_Angle,by=Darkness), data = comp_data_near_3)
# speed_gam_dca_fa <- gam(Speed_Diff ~ s(Distance,cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
# speed_gam_dca_fd <- gam(Speed_Diff ~ s(Distance,cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
# speed_gam_dca_fda <- gam(Speed_Diff ~ s(Distance,cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# speed_gam_dsa <- gam(Speed_Diff ~ s(Distance,sin_Angle), data = comp_data_near_3)
# speed_gam_dsa_f <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Flow), data = comp_data_near_3)
# speed_gam_dsa_a <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Ablation), data = comp_data_near_3)
# speed_gam_dsa_d <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Darkness), data = comp_data_near_3)
# speed_gam_dsa_fa <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
# speed_gam_dsa_fd <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
# speed_gam_dsa_fda <- gam(Speed_Diff ~ s(Distance,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# speed_gam_dcasa <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle), data = comp_data_near_3)
# speed_gam_dcasa_f <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle,by=Flow), data = comp_data_near_3)
# speed_gam_dcasa_a <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle,by=Ablation), data = comp_data_near_3)
# speed_gam_dcasa_d <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle,by=Darkness), data = comp_data_near_3)
# speed_gam_dcasa_fa <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
# speed_gam_dcasa_fd <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
# speed_gam_dcasa_fda <- gam(Speed_Diff ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)

speed_AIC <- AIC(speed_gam_d,speed_gam_d_f,speed_gam_d_a,speed_gam_d_d,speed_gam_d_fa,speed_gam_d_fd,speed_gam_d_fda,
                 speed_gam_ca,speed_gam_ca_f,speed_gam_ca_a,speed_gam_ca_d,speed_gam_ca_fa,speed_gam_ca_fd,speed_gam_ca_fda,
                 speed_gam_sa,speed_gam_sa_f,speed_gam_sa_a,speed_gam_sa_d,speed_gam_sa_fa,speed_gam_sa_fd,speed_gam_sa_fda,
                 speed_gam_dca,speed_gam_dca_f,speed_gam_dca_a,speed_gam_dca_d,speed_gam_dca_fa,speed_gam_dca_fd,speed_gam_dca_fda,
                 speed_gam_dsa,speed_gam_dsa_f,speed_gam_dsa_a,speed_gam_dsa_d,speed_gam_dsa_fa,speed_gam_dsa_fd,speed_gam_dsa_fda,
                 speed_gam_dcasa,speed_gam_dcasa_f,speed_gam_dcasa_a,speed_gam_dcasa_d,speed_gam_dcasa_fa,speed_gam_dcasa_fd,speed_gam_dcasa_fda)

speed_AIC <- tibble::rownames_to_column(speed_AIC, "Model_Name")

speed_AIC <- speed_AIC %>% mutate(Model_Name = fct_reorder(Model_Name, -AIC)) %>% arrange(AIC)

ggplot(speed_AIC, aes(x = Model_Name, y = AIC)) +
  geom_point(color = "blue") +
  xlab("") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  theme_light()+
  scale_y_reverse() +
  coord_flip()

speed_AIC
```

How we do that for the cosine of the headings

```{r}
# cos_heading_gam_d <- gam(cos_Heading ~ s(Distance), data = comp_data_near_3)
# cos_heading_gam_d_f <- gam(cos_Heading ~ s(Distance,by=Flow), data = comp_data_near_3)
# cos_heading_gam_d_a <- gam(cos_Heading ~ s(Distance,by=Ablation), data = comp_data_near_3)
# cos_heading_gam_d_d <- gam(cos_Heading ~ s(Distance,by=Darkness), data = comp_data_near_3)
# cos_heading_gam_d_fa <- gam(cos_Heading ~ s(Distance,by=Flow_Ablation), data = comp_data_near_3)
# cos_heading_gam_d_fd <- gam(cos_Heading ~ s(Distance,by=Flow_Darkness), data = comp_data_near_3)
# cos_heading_gam_d_fda <- gam(cos_Heading ~ s(Distance,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# cos_heading_gam_ca <- gam(cos_Heading ~ s(cos_Angle), data = comp_data_near_3)
# cos_heading_gam_ca_f <- gam(cos_Heading ~ s(cos_Angle,by=Flow), data = comp_data_near_3)
# cos_heading_gam_ca_a <- gam(cos_Heading ~ s(cos_Angle,by=Ablation), data = comp_data_near_3)
# cos_heading_gam_ca_d <- gam(cos_Heading ~ s(cos_Angle,by=Darkness), data = comp_data_near_3)
# cos_heading_gam_ca_fa <- gam(cos_Heading ~ s(cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
# cos_heading_gam_ca_fd <- gam(cos_Heading ~ s(cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
# cos_heading_gam_ca_fda <- gam(cos_Heading ~ s(cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# cos_heading_gam_sa <- gam(cos_Heading ~ s(sin_Angle), data = comp_data_near_3)
# cos_heading_gam_sa_f <- gam(cos_Heading ~ s(sin_Angle,by=Flow), data = comp_data_near_3)
# cos_heading_gam_sa_a <- gam(cos_Heading ~ s(sin_Angle,by=Ablation), data = comp_data_near_3)
# cos_heading_gam_sa_d <- gam(cos_Heading ~ s(sin_Angle,by=Darkness), data = comp_data_near_3)
# cos_heading_gam_sa_fa <- gam(cos_Heading ~ s(sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
# cos_heading_gam_sa_fd <- gam(cos_Heading ~ s(sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
# cos_heading_gam_sa_fda <- gam(cos_Heading ~ s(sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# cos_heading_gam_dca <- gam(cos_Heading ~ s(Distance,cos_Angle), data = comp_data_near_3)
# cos_heading_gam_dca_f <- gam(cos_Heading ~ s(Distance,cos_Angle,by=Flow), data = comp_data_near_3)
# cos_heading_gam_dca_a <- gam(cos_Heading ~ s(Distance,cos_Angle,by=Ablation), data = comp_data_near_3)
# cos_heading_gam_dca_d <- gam(cos_Heading ~ s(Distance,cos_Angle,by=Darkness), data = comp_data_near_3)
# cos_heading_gam_dca_fa <- gam(cos_Heading ~ s(Distance,cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
# cos_heading_gam_dca_fd <- gam(cos_Heading ~ s(Distance,cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
# cos_heading_gam_dca_fda <- gam(cos_Heading ~ s(Distance,cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# cos_heading_gam_dsa <- gam(cos_Heading ~ s(Distance,sin_Angle), data = comp_data_near_3)
# cos_heading_gam_dsa_f <- gam(cos_Heading ~ s(Distance,sin_Angle,by=Flow), data = comp_data_near_3)
# cos_heading_gam_dsa_a <- gam(cos_Heading ~ s(Distance,sin_Angle,by=Ablation), data = comp_data_near_3)
# cos_heading_gam_dsa_d <- gam(cos_Heading ~ s(Distance,sin_Angle,by=Darkness), data = comp_data_near_3)
# cos_heading_gam_dsa_fa <- gam(cos_Heading ~ s(Distance,sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
# cos_heading_gam_dsa_fd <- gam(cos_Heading ~ s(Distance,sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
# cos_heading_gam_dsa_fda <- gam(cos_Heading ~ s(Distance,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# cos_heading_gam_dcasa <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle), data = comp_data_near_3)
# cos_heading_gam_dcasa_f <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow), data = comp_data_near_3)
# cos_heading_gam_dcasa_a <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Ablation), data = comp_data_near_3)
# cos_heading_gam_dcasa_d <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Darkness), data = comp_data_near_3)
# cos_heading_gam_dcasa_fa <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
# cos_heading_gam_dcasa_fd <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
# cos_heading_gam_dcasa_fda <- gam(cos_Heading ~ s(Distance,cos_Angle,sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)

cos_heading_AIC <- AIC(cos_heading_gam_d,cos_heading_gam_d_f,cos_heading_gam_d_a,cos_heading_gam_d_d,cos_heading_gam_d_fa,cos_heading_gam_d_fd,cos_heading_gam_d_fda,
                 cos_heading_gam_ca,cos_heading_gam_ca_f,cos_heading_gam_ca_a,cos_heading_gam_ca_d,cos_heading_gam_ca_fa,cos_heading_gam_ca_fd,cos_heading_gam_ca_fda,
                 cos_heading_gam_sa,cos_heading_gam_sa_f,cos_heading_gam_sa_a,cos_heading_gam_sa_d,cos_heading_gam_sa_fa,cos_heading_gam_sa_fd,cos_heading_gam_sa_fda,
                 cos_heading_gam_dca,cos_heading_gam_dca_f,cos_heading_gam_dca_a,cos_heading_gam_dca_d,cos_heading_gam_dca_fa,cos_heading_gam_dca_fd,cos_heading_gam_dca_fda,
                 cos_heading_gam_dsa,cos_heading_gam_dsa_f,cos_heading_gam_dsa_a,cos_heading_gam_dsa_d,cos_heading_gam_dsa_fa,cos_heading_gam_dsa_fd,cos_heading_gam_dsa_fda,
                 cos_heading_gam_dcasa,cos_heading_gam_dcasa_f,cos_heading_gam_dcasa_a,cos_heading_gam_dcasa_d,cos_heading_gam_dcasa_fa,cos_heading_gam_dcasa_fd,cos_heading_gam_dcasa_fda)

cos_heading_AIC <- tibble::rownames_to_column(cos_heading_AIC, "Model_Name")

cos_heading_AIC <- cos_heading_AIC %>% mutate(Model_Name = fct_reorder(Model_Name, -AIC)) %>% arrange(AIC)

ggplot(cos_heading_AIC %>% arrange(AIC), aes(x = Model_Name, y = AIC)) +
  geom_point(color = "blue") +
  xlab("") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  theme_light() +
  scale_y_reverse() +
  coord_flip()

cos_heading_AIC
```

Now with the sin of the Headings
```{r}
# sin_heading_gam_d <- gam(sin_Heading ~ s(Distance), data = comp_data_near_3)
# sin_heading_gam_d_f <- gam(sin_Heading ~ s(Distance,by=Flow), data = comp_data_near_3)
# sin_heading_gam_d_a <- gam(sin_Heading ~ s(Distance,by=Ablation), data = comp_data_near_3)
# sin_heading_gam_d_d <- gam(sin_Heading ~ s(Distance,by=Darkness), data = comp_data_near_3)
# sin_heading_gam_d_fa <- gam(sin_Heading ~ s(Distance,by=Flow_Ablation), data = comp_data_near_3)
# sin_heading_gam_d_fd <- gam(sin_Heading ~ s(Distance,by=Flow_Darkness), data = comp_data_near_3)
# sin_heading_gam_d_fda <- gam(sin_Heading ~ s(Distance,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# sin_heading_gam_ca <- gam(sin_Heading ~ s(cos_Angle), data = comp_data_near_3)
# sin_heading_gam_ca_f <- gam(sin_Heading ~ s(cos_Angle,by=Flow), data = comp_data_near_3)
# sin_heading_gam_ca_a <- gam(sin_Heading ~ s(cos_Angle,by=Ablation), data = comp_data_near_3)
# sin_heading_gam_ca_d <- gam(sin_Heading ~ s(cos_Angle,by=Darkness), data = comp_data_near_3)
# sin_heading_gam_ca_fa <- gam(sin_Heading ~ s(cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
# sin_heading_gam_ca_fd <- gam(sin_Heading ~ s(cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
# sin_heading_gam_ca_fda <- gam(sin_Heading ~ s(cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# sin_heading_gam_sa <- gam(sin_Heading ~ s(sin_Angle), data = comp_data_near_3)
# sin_heading_gam_sa_f <- gam(sin_Heading ~ s(sin_Angle,by=Flow), data = comp_data_near_3)
# sin_heading_gam_sa_a <- gam(sin_Heading ~ s(sin_Angle,by=Ablation), data = comp_data_near_3)
# sin_heading_gam_sa_d <- gam(sin_Heading ~ s(sin_Angle,by=Darkness), data = comp_data_near_3)
# sin_heading_gam_sa_fa <- gam(sin_Heading ~ s(sin_Angle,by=Flow_Ablation), data = comp_data_near_3)
# sin_heading_gam_sa_fd <- gam(sin_Heading ~ s(sin_Angle,by=Flow_Darkness), data = comp_data_near_3)
# sin_heading_gam_sa_fda <- gam(sin_Heading ~ s(sin_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# sin_heading_gam_dca <- gam(sin_Heading ~ s(Distance,cos_Angle), data = comp_data_near_3)
# sin_heading_gam_dca_f <- gam(sin_Heading ~ s(Distance,cos_Angle,by=Flow), data = comp_data_near_3)
# sin_heading_gam_dca_a <- gam(sin_Heading ~ s(Distance,cos_Angle,by=Ablation), data = comp_data_near_3)
# sin_heading_gam_dca_d <- gam(sin_Heading ~ s(Distance,cos_Angle,by=Darkness), data = comp_data_near_3)
# sin_heading_gam_dca_fa <- gam(sin_Heading ~ s(Distance,cos_Angle,by=Flow_Ablation), data = comp_data_near_3)
# sin_heading_gam_dca_fd <- gam(sin_Heading ~ s(Distance,cos_Angle,by=Flow_Darkness), data = comp_data_near_3)
# sin_heading_gam_dca_fda <- gam(sin_Heading ~ s(Distance,cos_Angle,by=Flow_Ablation_Darkness), data = comp_data_near_3)
# 
# sin_heading_gam_dsa <- gam(sin_Heading ~ s(Distance,sin_Angle), data = comp_data_near_3)
# sin_heading_gam_dsa_f <- gam(sin_Heading ~ s(Distance,sin_Angle,by=Flow), data = comp_data_near_3)
# sin_heading_gam_dsa_a <- gam(sin_Heading ~ s(Distance,sin_Angle,by=Ablation), data = comp_data_near_3)
# sin_heading_gam_dsa_d <- gam(sin_Heading ~ s(Distance,sin_Angle,by=Darkness), data = comp_data_near_3)
